Supplementary Appendix

### 2025-07-23 paper/preprint/appendix.tex
one final render:

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-train-default}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-eval-default}: Evaluation Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-tune-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-tune-eval}: Evaluation Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-tune_lr-train}: Training Phase}]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, arc=.35mm, titlerule=0mm, colback=white, leftrule=.75mm, opacityback=0, colframe=quarto-callout-note-color-frame, breakable, toprule=.15mm, left=2mm, opacitybacktitle=0.6, bottomrule=.15mm, bottomtitle=1mm, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}]

@@

All computations were performed in the Julia Programming Language
(\citeproc{ref-bezanson2017julia}{Bezanson et al. 2017}). We have
developed a package for counterfactual training that leverages and
extends the functionality provided by several existing packages, most
notably
\href{https://github.com/JuliaTrustworthyAI/CounterfactualExplanations.jl}{CounterfactualExplanations.jl}
(\citeproc{ref-altmeyer2023explaining}{Altmeyer, Deursen, and Liem
2023}) and the \href{https://fluxml.ai/Flux.jl/v0.16/}{Flux.jl} library
for deep learning (\citeproc{ref-innes2018fashionable}{Michael Innes et
al. 2018}; \citeproc{ref-innes2018flux}{Mike Innes 2018}). We chose to
work with
\href{https://github.com/JuliaTrustworthyAI/CounterfactualExplanations.jl}{CounterfactualExplanations.jl}
because it currently appears to be the most comprehensive and extensible
package for counterfactual explanations. Despite its good interplay with
Flux.jl, the package is not, however, optimized to be used in training.
This has caused some issues with memory management and bottlenecked
performance. All of our code will be provided to reviewers of this work
and open-sourced upon publication.

>>>>

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-default}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-eval-default}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune_lr-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

All computations were performed in the Julia Programming Language
(\citeproc{ref-bezanson2017julia}{Bezanson et al. 2017}). We have
developed a package for counterfactual training that leverages and
extends the functionality provided by several existing packages, most
notably
\href{https://github.com/JuliaTrustworthyAI/CounterfactualExplanations.jl}{CounterfactualExplanations.jl}
(\citeproc{ref-altmeyer2023explaining}{Altmeyer, Deursen, and Liem
2023}) and the \href{https://fluxml.ai/Flux.jl/v0.16/}{Flux.jl} library
for deep learning (\citeproc{ref-innes2018fashionable}{Michael Innes et
al. 2018}; \citeproc{ref-innes2018flux}{Mike Innes 2018}). We chose to
work with
\href{https://github.com/JuliaTrustworthyAI/CounterfactualExplanations.jl}{CounterfactualExplanations.jl}
because it currently appears to be the most comprehensive and extensible
package for counterfactual explanations. Despite its good interplay with
Flux.jl, the package is not, however, optimized to be used in training.
This has caused some issues with memory management and bottlenecked
performance. All of our code will be provided to reviewers of this work
and open-sourced upon publication. The code is commented with clearly
marked references to the paper (look for
\texttt{\#\ -\/-\/-\/-\/-\ PAPER\ REF\ -\/-\/-\/-\/-}).
